---
title: "Lab 01 - Hello R"
author: "Thomas Monahan"
date: "9/6/21"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

```{r}
?datasaurus_dozen
```
Datasaurus_dozen has 1846 rows and 3 columns. 

### Exercise 2

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
We find that the correlation between x and y is -.06447185. 
### Exercise 3

```{r}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
```

```{r plot-star}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

We find that the correlation between x and y for the star data set is -.0629611.

### Exercise 4

We will now explore the circle data set!

Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
```

```{r plot-circle}
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
We find that the correlation between y and x for the circle data set is -.06834336. When we compare this with the correlation for the dino data we find:

```{r cor-circlevsdino}
circle_r = circle_data %>%
  summarize(r = cor(x, y)) 
dino_r = dino_data %>%
  summarize(r = cor(x, y)) 
(circle_r/dino_r)*100
```
We find that the r value for our circle data set is 6% greater than that of the dino data set. 
### Exercise 5

Plotting all datasets at once!

```{r fig.height=6, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Generating the summary coefficients:
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
